\section{Background}

\label{sec:background}

\subsection{The Information Aggregation Problem}

Consider the following problem within algorithmic mechanism design known as the
\emph{information aggregation problem}~\cite[Ch.~26]{AGTBook}. An individual
known as the ``aggregator'' wishes to obtain a prediction about an uncertain
variable which will be realised at some point in the future. There are a number
of individuals known as the ``informants'' who each hold sets of information
about the variable's outcome. The goal is to design a mechanism that extracts
the relevant information from the informants and uses it to provide a
prediction of the variable's realisation. In an ideal setting the mechanism
should produce the same prediction as an omniscient forecast that has access to
all information available to all informants. This may not be viable in
practice, since each agent's information is private information, and so the
mechanism must incentivise them to act in the desired truth-telling manner.

A prediction market is one mechanism that can provide such a forecast. In this
setting the aggregator creates a financial security whose payoff is tied to the
outcome of the variable. In the simpler case of binary events, such a security
may pay out \$1 for each share held if the variable has a ``true'' or ``yes''
outcome, and \$0 otherwise, however markets can be created for other types
including discrete (``will the result of the match be a home win, away win, or
a draw?''), continuous (``what will be the highest measured temperature in
Coventry in September?''), or any combination of these types. Informants are
then able to participate in the market induced by the security by trading
shares according to their beliefs: those who believe, for example, that global
warming is real might buy shares at a given price in the market, ``the global
average temperature in 2020 will be higher than that in 2019'', while deniers
may be inclined to sell shares. The share price will be adjusted accordingly,
and the aggregator can view the current price as the informant's combined
belief of the outcome of the event.

In this model there is a set $\Omega$ of possible states of the world and at
any moment the world is in exactly one state $\omega \in \Omega$, though the
informants do not know which. Each informant $i$ may however possess partial
information regarding this true state, and this is represented by a partition
$\pi_i$ of $\Omega$. The agent knows in which subset of this partition the true
world state lies, but does not know the exact member of which is true. Given
$n$ agents, their combined information $\hat{\pi}$ is the coarsest common
refinement of the partitions $\pi_1, \ldots, \pi_n$.\footnote{A partition
$\alpha$ of a set $X$ is a refinement of a partition $\rho$ of $X$ if every
element of $\alpha$ is a subset of some element of $\rho$. In this case
$\alpha$ is \emph{finer} than $\rho$ and $\rho$ is \emph{coarser} than
$\alpha$.}

We also assume a common prior probability distribution $P \in \Delta^{\Omega}$
which describes the probabilities that all agents assign to the different world
states before receiving any information. Once each agent receives their partial
information, they form their posterior beliefs by restricting the common prior
to the subset of their partition in which they know the true state to lie. For
our purposes, a \emph{forecast} is an estimate of the expected value of the
function $f : \Omega \rightarrow \{0,1\}$, known as an \emph{event}, which
equals one for exactly one subset of $\Omega$ and 0 otherwise.

As mentioned, there is an ideal ``omniscient'' forecast that uses the
distribution $P$ restricted to the subset of $\hat{\pi}$ in which the true
world state lies but which is impractical given the private nature of each
agent's information. The goal is therefore a mechanism to incentivise agents to
reveal their private information such that in equilibrium we achieve a forecast
as close as possible to the omniscient one. Prediction markets offer the agents
the chance of financial gain for revealing information regarding the expected
value of $f(\omega)$, and the share price of the security can be interpreted as
the collective forecast of the agents. In the following section we shall
outline some of the different approaches one can take to designing the market
mechanism itself: the best choice will vary for the setting and will depend on
what is tractable given the types of bets that are on offer.

In Section~\ref{sec:design} we shall
outline the different approaches one can take to designing the prediction
market mechanism itself and the one among them, a Market Scoring Rule, that we
implement. Importantly, Market Scoring Rules are one of the ways to increase
liquidity in the market as the system itself assumes the opposite side to any
trade, meaning users may participate even when no other user wishes to buy or
sell for what they are asking or bidding. This means a trade is always able to
be executed, although without care the system could make consistent losses.

\subsection{Combinatorial Prediction Markets}

A \emph{combinatorial} prediction market is one in which the total state space
$\Omega$ is the product space of a collection of base events. Suppose knowing
the outcome of a given event cannot be predicted with certainty even if the
outcomes to all other base events are known, and we wish to provide the
opportunity to trade on any outcome $\omega \in \Omega$: with a set of base
events of size $\mathcal{|E|}$ we would have a total outcome space of size
$2^\mathcal{|E|}$.  With such a large outcome space it may therefore be
impossible to even all the securities available in such a market. Combinatorial
markets can make use of ``expressive'' bidding languages that represent
collections of securities succinctly, including \emph{compound orders} and
\emph{combined orders}.

Combined orders allow a user to trade a collection of securities by specifying
the securities they wish to buy or sell together as a bundle along with limit
prices for each constituent security. If there is even a single security in the
bundle that is not at least as ``good''\footnote{If we are buying we want a
price less than or equal to the limit price, while the opposite is true if we
are selling.} as its limit price, then no trade is made. Consider an agent's
alternative if they wish to trade on all these securities in a
non-combinatorial market: this means they would need to trade on each one
individually. Throughout the execution of such a sequence of trades, however,
market prices are subject to change, and in the worst case these could reduce
or even reverse the utility of participating in such trades. Combined orders
therefore protect its participants from such risk. Calculating assignments of
securities to buyers in such a setting is reminiscent of the challenge faced
in a combinatorial \emph{auction}, which known to be NP-hard.

Compound orders are generalisations of combined orders and allow users to trade
on any Boolean expression involving the set of base events. Now again the size
of the outcome space is $2^\mathcal{|E|}$, but now users may select any
collection of these worlds to bet on, giving a total of $2^{2^\mathcal{|E|}}$
options. Agents now place orders by requesting $q$ shares of the security
$S_{\phi|\psi}$ at share price $p$, where $S_{\phi|\psi}$ pays out \$1 if both
Boolean formulae $\phi$ and $\psi$ are true, \$0 if only $\psi$ is true, and
refunds the user if $\psi$ is false. These orders will yield a payoff
$\gamma^{\langle \omega \rangle}$ depending on the state $\omega \in \Omega$,
and can be written as:
$$
\gamma^{\langle \omega \rangle} = q \cdot \mathds{1}_{\omega \in \psi}
(\mathds{1}_{\omega \in \phi} - p)
$$

in which $\omega \in \phi$ means outcome $\omega$ satisfies the Boolean formula
$\phi$. This says that the order will receive an overall payoff of zero if the
true world state $\omega$ does satisfy $\psi$, meaning the order is invalid and
refunded to the user. Otherwise, the user will receive a payout of $(1-p)$ for
each share they bought if $\omega$ satisfies $\phi$. If the event does not
occur they will lose what they paid and receive a payoff of $-p$ for each of
$q$ shares. Each user $i$ has a payoff vector $\gamma_i$ induced by submitting
orders. It is the job of the auctioneer to determine which orders to accept:
let $\alpha_i \in \{0,1\}$ indicate whether the auctioneer accepts an order
from user $i$. Since they will collect the money paid by the trader and payout
their winnings according to each user's payoff vector, the auctioneer receives
payoff: $$ \gamma_a = \sum_i -\alpha_i \gamma_i $$

The \emph{indivisible matching problem} is the problem that, given a set of
orders, does there exist a set of $\alpha_i \in \{0,1\}$ and $\sum_i \alpha_i
\ge 1$ such that for any outcome $\omega$ the auctioneer receives payoff
$\gamma_a^{\langle \omega \rangle} \ge 0$? In other words, the auctioneer is
looking to accept some bundle of orders \emph{without risk}.

\subsubsection*{Example}

Suppose $\mathcal{E} = \{X_1, X_2\}$ and there are two orders: agent 1 wishes
to buy two shares of security $S_{X_1}$ at 0.6 per share while agent 2 wishes
to sell one shares of security $S_{X_1,X_2}$ for 0.2 per share. Assuming the
auctioneer accepts both orders, the payoffs are as follows (note player 2's
payoff vector is negated since they are selling):
%
\begin{equation*}
	\begin{aligned}
		\gamma_1 & = \left\langle \begin{matrix}
			\gamma_1^{X_1,X_2} &
			\gamma_1^{X_1,\bar{X_2}} &
			\gamma_1^{\bar{X_1},X_2} &
		\gamma_1^{\bar{X_1},\bar{X_2}} \end{matrix} \right\rangle 
%
		 = \left\langle \begin{matrix}
			2(1-0.6) & 2(1-0.6) & 2(-0.6) & 2(-0.6) \end{matrix} \right\rangle \\
%
		\gamma_2 & = - \left\langle \begin{matrix}
			1(1-0.2) & 1(-0.2) & 1(-0.2) & 1(-0.2) \end{matrix} \right\rangle \\
%
		\gamma_a & = \left\langle \begin{matrix}
			0 & -1 & 1 & 1 \end{matrix} \right\rangle
	\end{aligned}
\end{equation*}

Accepting both orders is therefore not a valid solution to the indivisible
matching problem since in the event that $\omega = \{X_1,\bar{X_2}\}$ the
auctioneer would have to run a loss. In fact, finding a solution to the
indivisible matching problem is NP-complete~\cite[Ch.~26]{AGTBook}. Although we
do not focus on combinatorial prediction markets in this project, it is useful
to illustrate the challenges of designing efficient market mechanisms. In
particular, we are concerned with illiquidity, which arises when there is too
little interaction for a trade to be executed.

\subsection{Trading Mechanisms}

\label{sec:tradingMechanisms}

\subsubsection{Continuous Double Auctions}

Trading mechanisms are responsible for deciding which trades are executed, in
what quantities, and at which price points. In the previous section, although
users had to submit orders of a particular form, the auctioneer was free to
accept any subset of the orders received: this section expounds upon \emph{how}
trades may be chosen. There are numerous methods of implementing market trading
mechanisms, including double auctions, market call auctions, and automated
market makers. A Continuous Double Auction (CDA) is a method by which buyers
are matched with sellers of a stock or security. The market maker keeps an
order book that tracks the bids, submitted by those looking to buy, and the
asks, submitted by those looking to sell. Traders arrive asynchronously and
place orders, and when two opposite orders match the trade is executed. CDAs
are traditionally used in highly liquid markets, such as the New York Stock
Exchange, where there are many bids for a given ask and vice versa. An issue
with this approach is that it relies on high liquidity, as it requires that
there is always a willing buyer and seller at a particular price and quantity
in order to a trade to execute. In prediction markets there are far fewer
participants than in a stock exchange, and this problem is made worse in
combinatorial markets, in which case a trader's attention is split among an
exponential number of securities making the likelihood that a buyer and seller
are looking to trade on the same event exceptionally small. Prices may also not
be informative of the true beliefs held by traders in CDAs: since all traders
can see bids and asks as they are submitted sellers may be encouraged to ask
less than what they truly believe a security's ``true'' value to be in order to
beat out another seller and make a profit. This is not useful in a prediction
market setting, where we want to elicit the true beliefs from users.

These problems arising from market illiquidity can be averted by using an
automated market maker, in which a price maker is nearly always willing to
accept both buy and sell orders at a certain price. Participation in the market
will have an effect on these prices, the exact nature of which will be down to
the market maker. This ensures that, if the price is desirable, participants
are always able to make a trade. An automated market maker is not typically
used in real-world markets since always assuming the opposite side to any trade
would likely result in significant losses for ``the house''; in play-money
markets this is not such an issue as losses are less detrimental with no
real-world negative value. In general there are three properties that an
automated market maker should satisfy in order to be of practical use: traders
should have an incentive to participate in the market whenever their beliefs
would change the price; the computation of market prices should be tractable;
and the market's loss should be bounded. We have two options for implementing
automated market makers: as a parimutuel market or using a Market Scoring Rule.

\subsubsection{Parimutuel Markets}

In parimutuel markets traders wager money their choice of outcomes from a
mutually exclusive and exhaustive set. When the event's outcome is realised the
total wagered money is split between those who wagered correctly, in proportion
to the size of their bet. In order to accommodate traders selling shares prior
to the outcome of the event, \emph{dynamic} parimutuel markets incorporate a
cost function that varies the price of a single share due to trading activity.
An example of one such cost function is the share-ratio cost function. Suppose
we have an outcome space $\Omega$ and let $q_j$ denote the total number of
shares for event $j \in \Omega$. Let $\vect{q} = (q_1, \ldots, q_{|\Omega|})$
be the vector of outstanding shares of all contracts. The share-ratio cost
function is:
%
$$ C(\vect{q}) = \sqrt{\sum_j q_j^2} $$

A trader wishing to buy $q_j' - q_j$ shares of security $j$, who changes the
number of outstanding shares of $j$ from $q_j$ to $q_j'$, pays the market
$C(\vect{q}_{-j}, q_j') - C(\vect{q})$.\footnote{We use $\vect{q}_{-j}$ to
denote the vector $(q_1, \ldots, q_{j-1}, q_{j+1}, \ldots, q_{|\Omega|})$.}
There is a corresponding price function $p_j$ that gives the price for
purchasing an infinitesimal quantity of shares in security $j$ and is used to
quote a share price to market participants:
%
$$ p_j = \frac{q_j}{\sum_k q_k^2} $$

This share price $p_j$ should not be used to calculate the cost of a
transaction since an agent's participation in the market will instantly change
this value. The purpose of a prediction market is to elicit private information
on some future event: we can calculate the probability $\pi_j$ of outcome $j$ using
information about the activity within the market: $\pi_j = p_j^2$.

\subsubsection{Scoring Rule Markets}

A scoring rule is used to assign probabilities to a set of mutually exclusive
outcomes. When the scoring rule is proper, it can be converted to an automated
market maker that uses a Market Scoring Rule (MSR). Again at the heart of a MSR
is the cost function $C(\vect{q})$, which is a means of recording the total
amount of money spent in the market by traders as a function of the total
number of shares in circulation. Traders wishing to purchase $q_j' - q_j$
shares of security $j$ must again pay $C(\vect{q}_{-j}, q_j')-C(\vect{q})$.
Note that in both parimutuel markets and scoring rule markets, these
rules encode sell transactions as well, in which case $q_j' < q_j$. We cannot
use $C$ directly to quote a share price to the user since we first need to know
what quantity they to buy or sell: we use its derivative $p = \partial C /
\partial q_j$ to again quote the cost for an infinitesimal quantity of shares. 
As an example, the quadratic scoring rule gives the reward $Q(\vect{r},i)$ if
the $i$th event occurs, given the probability vector $\vect{r}$. The cost
function corresponding to the quadratic scoring rule is:
%
$$
C(\vect{q}) =
\frac{\sum_j q_j}{|\Omega|} + \frac{\sum_j q_j^2}{4b}  +
\frac{\left( \sum_j q_j \right)^2}{4b|\Omega|} - \frac{b}{|\Omega|}
$$

Scoring rule markets pay typically pay out \$1 for each share held of a
security whose outcome was positive, and \$0 otherwise. In contrast, parimutuel
markets can have a different payoff per share since they pay out an equal
portion of the total amount wagered per share held to winning shareholders. In
this project we implement the former. The following section will outline some
existing prediction markets as well as important results from the literature.
