\section{Design}

% different types of market:
% - market scoring rule
% - call market auction
% - continuous double auction
% - bookmaker
% - parimutuel market

\label{sec:design}

\subsection{Mechanism Overview}

As mentioned our design of the prediction market is based on the peer
prediction mechanism proposed by Freeman et al.~\cite{Freeman2017}. In this
section we will outline the main ideas presented in their work and give an
overview of the peer prediction mechanism.

We are interested in setting up a prediction market for outcome of a binary
random variable $X \in \{0,1\}$. We will use the terms ``market'', ``stock'',
and ``security'' interchangeably throughout to refer to the entity comprising a
wager, such as ``Arsenal will beat Tottenham'', and a deadline -- these two
pieces of information are all we need to represent the event $X$. The mechanism
is divided into two main stages: the market stage, where users may buy and sell
shares in the securities whose deadlines have not yet passed; and the
arbitration stage, where a subset of the users report on the outcome of the
security and the payout price per share is computed. In a traditional
prediction market on binary events, if the market's outcome was positive then
stakeholders with long positions will then be paid out \$1 for each share they
own while those with short positions will buy back their shares at a price of
\$1 per share. Similarly, if the outcome was negative, long users will have
lost money since they receive no money back from their initial investment,
while short users will profit as they must ``buy back'' their shares at a price
of \$0 per share. This market is different in that market outcomes are set as
the proportion of arbiters that reported a positive outcome. Therefore, even if a
user has gone long on a security, this must have been at or below the right
price to make a profit, since it is not necessarily the case that 100\% of the
users reporting on the market agree on its outcome.

Since we rely heavily on user participation for the mechanism to run correctly,
it is important that users act in the desired manner. This mechanism
incentivises users to act truthfully in two aspects: firstly, users are
encouraged to trade on their belief of the market's realised outcome, rather
than, for example, how a specific news source will report on it, since the
outcome is determined entirely by the community and each arbiter will have
access to their own news sources of varying biases; secondly, it is in a user's
best interests to report on market outcomes truthfully, since they can receive
no better payoff by attempting to manipulate the system, regardless of whether
they hold a position in the market. Therefore, we are able to gather accurate
public sentiment on the event itself as well as its outcome, and ambiguous
securities are dealt with more gracefully.

These considerations also allow us to achieve certain useful guarantees. For
example, in order to incentivise reporters to act truthfully, we must pay them
more than what they would otherwise gain from attempting to manipulate the
system. We can use this knowledge, coupled with what we know stakeholders are
expecting to be paid out, to bound the amount we must pay to ensure incentive
compatibility. Thus we can ensure that the system is sustainable and the
system's loss is bounded.

In the following sections, we shall outline the mechanism we implement from a
theoretical standpoint. 

\subsection{Market Stage}

\label{sec:marketStage}

\subsubsection{Trading Mechanism}

The market stage allows users to create markets for any bet they desire and
specifies the how the share price reacts according to user participation. As we
implement a decentralised market, we place no restriction on the bet that can
be placed other than that its outcome must be binary. As we mention in
Section~\ref{sec:tradingMechanisms}, we implement a scoring rule market, in
which users must pay $C(\vect{q}_{-j}, q_j')-C(\vect{q})$ to change the total
number of outstanding shares of security $j$ from $q_j$ to $q_j'$.  Since
market prices are dynamic we quote instantaneous share price to users with its
derivative $p_j$ -- this is also used to calculate the trading fee on a given
transaction, which raises funds to pay arbiters in the following stage of the
mechanism.

\subsubsection{Trading fees}

In addition to calculating transaction costs and share prices via the MSR, the
market stage is responsible for implementing trading fees. As mentioned, the
mechanism we implement is not budget balanced, meaning the market must be
subsidised in order to pay arbiters for submitting outcome reports. Trading
fees raise these subsidies. For any given market, buying shares will push the
share price $p$ upwards towards \$1, while selling shares will push it towards
\$0. There are two types of transactions that a user may be involved in: one in
which a trader is increasing their risk, and one in which a user is liquidating
shares it has previously bought or sold. For example, suppose Alice holds ten
shares in a particular security: if she were to sell up to and including ten
shares she would simply be liquidating shares that have already been sold to
her, while if she were to buy additional shares or sell more than ten, then she
would be increasing her risk. Risk transactions are defined analogously for a
user buying shares. Trading fees are only imposed on transactions in which a
user increases their risk, and can be viewed as a fee on their worst-case loss.
Specifically, for fixed system parameter $f$ and for transactions in which a
user increases their risk, a buy transaction that pushes share price to $p$
incurs an additional charge of $fp$, while a sell transaction that pushes share
price to $p$ incurs additional charge of $f(1-p)$. These fees also allow us to
bound the maximum payout we must pay to a stakeholder, since they bound share
prices away from \$0 and \$1. Users may trade shares in a given security as
long as they have enough funds to make the transaction (including the fee), and
as long as the deadline has not yet passed. After the market expires,
stakeholders' positions are final and we then determine the outcome of the
market via peer prediction in the arbitration stage.

\subsection{Arbitration Stage}

\subsubsection{Outcome Reporting}

The arbitration stage is concerned with determining the perceived outcome of
the event $X$ from a subset of the community, known as arbiters, who offer
reports on the outcome they observed. Specifically, each arbiter $i$ receives a
private signal $x_i \in \{0,1\}$ that tells them the result of the event --
this is analogous to reading the news, watching the match, even hearing about
it from a friend, and will vary from market to market. The arbiter then submits
a report $\hat{x}_i \in \{0,1\}$ to the system that tells it what they believe
to be the outcome. Since the signal they receive is private information, we
have no way of determining whether this report is what they truly observed or
whether they are lying. Instead, we incentivise arbiters to act truthfully by
paying them a reward if their report agrees with another randomly chosen
arbiter: for this we implement the ``1/prior with midpoint'' mechanism, which
we will detail below.

Once all reports have been collected and the arbiters paid, the outcome of the
market $\hat{X} \in [0,1]$ is set to the proportion of arbiters that reported a
positive outcome. This differs from traditional prediction markets, in which
shares of a security will pay out \$1 if the event occurred, and \$0 otherwise.
Stakeholders are then paid out in the usual manner, where those with long
positions are paid out $\hat{X}$ for each share owned, while those with short
positions must buy them back at $\hat{X}$ per share. This should not change how
traders view the security: if they have information telling them the event will
occur they will still buy into the market if the share price is appropriate,
while if they believe the event is unlikely they will continue to sell. The
mechanism simply accommodates for the possibly ambiguous bets made by the
community.

\subsubsection{1/prior mechanism}

We use a modified version of the 1/prior payment mechanism to reward users for
submitting reports on an event's outcome and to incentivise truth telling
behaviour. The original version was conceived by Jurca and
Faltings~\cite{JurcaFaltings2008, JurcaFaltings2011} as a means of rewarding
arbiters for participation in opinion polls, another means of crowdsourcing a
forecast in which users submit probabilistic estimates for the likelihood of
events to occur. Witkowski~\cite{Witkowski2014} then generalised this to pay
out different amounts depending on the signals reported by paired arbiters. For
arbiters $i$ and $j$ with reports $\hat{x}_i$ and $\hat{x}_j$, the 1/prior
mechanism pays a reward $u(\hat{x}_i, \hat{x}_j)$ as follows:
%
\begin{equation}
	\label{eq:oneOverPrior}
	u(\hat{x}_i, \hat{x}_j) =
	\begin{cases}
		k \mu & \text{if } \hat{x}_i = \hat{x}_j = 0 \\
		k (1-\mu) & \text{if } \hat{x}_i = \hat{x}_j = 1 \\
		0 & \text{otherwise}
	\end{cases}
\end{equation}

In this, $k$ is a parameter and $\mu$ is the common prior belief that $X=1$. A
suitable value to use for $\mu$ in our case is the closing price of the market:
if users feel the event is likely to occur they will buy shares of it, pushing
the share price towards \$1, and if they feel it is unlikely it will be pushed
towards \$0. Everyone can see this price, and if it differs from a user's
beliefs they will participate in the market and alter the price accordingly,
making it a sensible choice for the common prior.

The modification introduced by Freeman et al.~\cite{Freeman2017} to the 1/prior
mechanism is simple and requires two additional values. Let $\mu_1^i$ be the
probability that, given that agent $i$ receives a positive signal of the
event's outcome, another randomly chosen user also receives a positive signal.
Similarly, let $\mu_0^i$ be the probability that, given that agent $i$ receives
a negative signal, another randomly chosen user receives a positive signal. We
require a common value for these ``update'' probabilities across all agents, so
we define the $\mu_1$ and $\mu_0$ as follows:
%
\begin{equation} \begin{gathered} \mu_1 := \min_i \mu_1^i \\ \mu_0 := \max_i
\mu_0^i \end{gathered} \end{equation}

The modified payment mechanism is now simply Equation~\ref{eq:oneOverPrior}
with $\mu$ replaced by $(\mu_1 + \mu_0)/2$. This is the
``1/prior-with-midpoint'' mechanism and guarantees that the incentives for
arbiters are always the same, no matter the signal they receive. The arbiter
with the greatest incentive to misreport -- that is, an arbiter with a large
stake in the market in which they are reporting -- has this incentive weakly
decreased by using replacing $\mu$ with the midpoint $(\mu_1 + \mu_0)/2$ in the
payment rule.

In particular, suppose arbiter $i$ holds a position of $n_i$ securities in the
market. We can ensure truthful reporting is a best response for $i$ by setting
the 1/prior-with-midpoint parameter $k$ to the appropriate value such that they
will receive weakly greater reward from the payment mechanism than they would
by misreporting. With $m$ arbiters and $\delta = \mu_1 - \mu_0$, truthful
reporting for arbiter $i$ is a best response if:
%
\begin{equation}
	\label{eq:kBoundN}
	k \ge \frac{2 |n_i|}{m \delta}
\end{equation}

\subsection{Tools}

In order to write our web application, we will need a platform on which to host
the server, the ability to define webpages, and a means of interacting with a
database for persistent storage. There are a number of useful packages provided
by Quicklisp that allows all of this functionality to be implemented in Lisp.
Using a single language to write the entire application -- as opposed to, say,
a combination of HTML, PHP, MySQL, and Javascript -- encourages a cleaner and
more flexible implementation and allows us to make full use of the tools
available to the language. A key advantage to using Lisp in particular is its
focus on extensibility, and specifically its powerful macro system allows us to
abstract away unnecessary details and write more generalised code. We discuss
this in greater detail in Section~\ref{sec:implementation}.

Our prediction market is written in the widely-used Common Lisp dialect of the
Lisp family of programming languages, and we use the Steel Bank Common Lisp
(SBCL) compiler and runtime environment to develop the code. Most importantly,
Common Lisp is well-supported by Quicklisp, which provides the following
packages that enable us to write the prediction market:

\begin{itemize}
	\item Hunchentoot \cite{Hunchentoot}
	\item CL-WHO \cite{CL-WHO}
	\item Mito \cite{Mito}
	\item SXQL \cite{SXQL}
	\item Parenscript \cite{Parenscript}
	\item Smackjack \cite{Smackjack}
\end{itemize}

Hunchentoot provides the environment on which we host the server and provides
automatic session handling, allowing us to implement a login system, easy
access of HTTP GET and POST parameters submitted via HTML forms, and a simple
interface through which to define webpage handlers. To generate the webpages
themselves we use CL-WHO\footnote{Common Lisp With HTML Output.}, which
translates Lisp expressions into HTML strings that we then pass to the
appropriate Hunchentoot functions. The structure of a Lisp program maps well to
that expected by an HTML file, while allowing us to dynamically generate pages
through the use of macros, making Lisp a suitable choice for this purpose.

Mito is an Object Relational Mapper (ORM) that provides an interface with which
we can connect and interact with a Relational Database Management System from
within the Lisp environment. We opt for a MySQL backend, simply due to its
familiarity, though this choice is largely immaterial given our simple
requirements. We can compose more complex MySQL statement using SXQL, and this
integrates well with Mito so that the two are effectively used as one library.

Parenscript allows us to incorporate Javascript into the site with the
intention of improving user experience. Currently it is used as a means of
performing client-side validation of form data, to ensure information arrives
at the server in the correct format and that all the necessary data is there.
It also enables us to use the Smackjack library, allowing us to have
asynchronous communication between the client and server. Particularly
important in any real-time market, this ensures all prices displayed to the
user are current and the user is interacting with an up-to-date state of the
system.

We use the Ngrok~\cite{ngrok} utility throughout the project's development to
tunnel ports on our local machine to public URLs, to ensure our market not only
functions locally but continues to do so on different machines and with
multiple users at once. Finally, Git and Github have been used extensively for
version control and remote storage and backup.
